A simulation study of gene flow and local polygenic adaptation motivated by threespine stickleback evolution

### 2018-10-22 Stickleback_Paper.tex
fixed header

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Sharing of freshwater adapted alleles}

%FIGURES THAT SHOW THIS:
%-MPAA / IND
%-Total/Avg shared
\begin{comment}
The tenfold difference in speed of adaptation occurs because at low migration rates, adaptation occurs independently in each lake,and the marine habitat has ten times the influx of new alleles than any one lake. In other words, greater mixing at higher migration rates allows lakes to share alleles instead of developing their own genetic basis of adaptation. As a first indication of this, Figure \ref{fig:Fst} shows that $F_{ST}$ between the ``original'' and ``introduced'' sets of lakes at effect mutations decreased with migration rate.

>>>>

\begin{comment}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Sharing of freshwater adapted alleles}

%FIGURES THAT SHOW THIS:
%-MPAA / IND
The tenfold difference in speed of adaptation occurs because at low migration rates, adaptation occurs independently in each lake,and the marine habitat has ten times the influx of new alleles than any one lake. In other words, greater mixing at higher migration rates allows lakes to share alleles instead of developing their own genetic basis of adaptation. As a first indication of this, Figure \ref{fig:Fst} shows that $F_{ST}$ between the ``original'' and ``introduced'' sets of lakes at effect mutations decreased with migration rate.
